\documentclass[11pt,oneside]{amsart}
\usepackage[margin=1in]{geometry}
\usepackage{amssymb,parskip,mathtools,microtype}
\usepackage[shortlabels]{enumitem}

\theoremstyle{definition}
\newtheorem{problem}{Problem}
\newtheorem{remark}{Remark}

\newcommand{\bC}{\mathbb{C}}
\newcommand{\bF}{\mathbb{F}}
\newcommand{\bQ}{\mathbb{Q}}
\newcommand{\bR}{\mathbb{R}}
\newcommand{\bZ}{\mathbb{Z}}
\newcommand{\bE}{\mathbb{E}}
\newcommand{\eps}{\varepsilon}

\DeclareMathOperator{\Var}{Var}
\let\Re\relax
\DeclareMathOperator{\Re}{Re}
\let\Im\relax
\DeclareMathOperator{\Im}{Im}
\DeclareMathOperator{\Arg}{Arg}

\title{MATH4460 Spring 2023\\
Practice Midterm 1}

\begin{document}
\maketitle

Most of these problems are from a past MATH4460 exam.

\begin{problem}
  For each of the following statements, determine whether it is true or false. No explanations need to be given.
  \begin{enumerate}[(a)]
    \item If $f$ is holomorphic at a point $z_0$, then $f$ is differentiable at $z_0$.
    \item The imaginary part of $\sqrt{17}\left( \cos\left( \frac{65\pi}{38} \right) +i\sin\left( \frac{65\pi}{38} \right)\right)^{19}$ is negative.
    \item The function $f(z)=\overline z^2$ is continuous on $\bC$.
    \item If $\Im(z)>0$, then $\Im(1/z)<0$.
    \item If $\pi/4<\Arg(z)<\pi/2$, then $3\pi/4<\Arg(z^3)<3\pi/2$.
  \end{enumerate}
\end{problem}

\begin{problem}
  Given the function $U(x,y)=xy-8x$ from $\bR^2$ to $\bR$, find a holomorphic function $f(z)$ whose real part is equal to $U$, or prove no such function exists.
\end{problem}

\begin{problem}
  Let $A=\{z\in\bC:|z-2+i|>3\}$.
  \begin{enumerate}[(a)]
    \item Graph $A$ in the complex plane.
    \item Is $A$ open?
    \item Determine the boundary of $A$.
  \end{enumerate}
\end{problem}

\begin{problem}
  Let $z,w$ be complex numbers with $|w|<1$ and $|z|<1$.
  \begin{enumerate}[(a)]
    \item Do you expect $(1-w\overline w)(1-z\overline z)$ to be positive or negative, or not enough information?
    \item Use the result from part (a) to show that
    \[\left|\frac{w-z}{1-\overline wz}\right|<1.\]
  \end{enumerate}
\end{problem}

\begin{problem}
  Find all solutions of the complex equation $2z^3+i=0$. Leave your answers in exponential form.
\end{problem}

\begin{problem}
  Find the image of the line $\{z\in\bC:\Im z=1\}$ under the mapping $f(z)=2/z$. Draw the image in the complex plane as well.
\end{problem}

\begin{problem}
  Let $f(z)$ be an analytic function defined on an open set $D\subseteq\bC$. Suppose that $e^{f(z)}$ is a real-valued function (i.e.\ no imaginary part). Prove that $f(z)$ is a constant.
\end{problem}

\newpage

\section{Remarks}
\begin{remark}
  \leavevmode\begin{enumerate}[(a)]
    \item True
    \item False. The number can be rewritten as $\sqrt{17}(e^{65\pi i/38})^{19}=\sqrt{17}e^{\pi i/2}$ which points up (it's $\sqrt{17}i$).
    \item True. $z\mapsto \overline z$ is continuous since it's $(x,y)\mapsto (x,-y)$ when interpreted as a function from $\bR^2$ to $\bR^2$, and squaring is continuous, and compositions of continuous functions are continuous.
    \item True. Direct computation.
    \item Would be true if $\Arg$ took values in $[0,2\pi)$. Since $\Arg$ takes values in $(\pi,\pi]$ in thie class, it's false.
  \end{enumerate}
\end{remark}

\begin{remark}
  If $V=\Im f$ then CR equations imply $V_x=-x$ and $V_y=y-8$. Your favorite multivariable method to find a potential function with gradient $(-x,y-8)$ gives $V(x)=-\frac 12x^2+\frac 12y^2-8y+C$, and any choice of $C$ works. Let's take $C=0$ and write $U+iV$ as a function of $z$. Here's how I do this last step. We know $z=x+yi$ and $z^2=(x^2-y^2)+2xyi$. Based on this, we can see that $8x$ is the real part of $8z$ and $xy$ is the real part of $-\frac 12iz^2$. So then $-\frac12iz^2+8z$ is our desired function.
\end{remark}

\begin{remark}
  We didn't rigorously define open sets in this class so there is really nothing to do in this problem. The picture of $A$ in the complex plane is the complement of a closed disk of radius 3 centered at $2-i$. The boundary is the circle of radius 3 centered at $2-i$.
\end{remark}

\begin{remark}
  $w\overline w=|w|$ and similarly with $z$, and so $0<1-w\overline w<1$ and $0<1-z\overline z<1$ meaning the answer to part (a) is positive.

  Part (b) is some algebraic manipulation.
\end{remark}

\begin{remark}
  $2z^3=-i=e^{3\pi i/2}\implies z^3=\frac 12 e^{3\pi i/2}\implies z=\frac 1{\sqrt[3]2}e^{\pi i/2+(2\pi i/3)k}$, $k\in\bZ$.
\end{remark}

\begin{remark}
  Expand out $2/(x+i)$, look at real and imaginary parts, and trace out the curve (where $x$ is the time parameter) in the plane.
\end{remark}

\begin{remark}
  Work it out with CR equations. Before diving in you might notice that $f(z)$ must be real-valued up to integer multiples of $2\pi i$, but since $f$ is continuous and the set of integer multiples of $2\pi i$ is discrete, the imaginary part of $f$ must be a constant multiple of $2\pi i$. Then it's a lot easier to show that the real part of $f$ must be constant as well.
\end{remark}

\end{document}
